\bibitem{das2013complex}Das, J., Chakraborty, S., Podder, S. \& Ghosh, T. Complex-forming proteins escape the robust regulations of miRNA in human. {\em FEBS Letters}. \textbf{587}, 2284-2287 (2013)
\bibitem{das2014insights}Das, J., Podder, S. \& Ghosh, T. Insights into the miRNA regulations in human disease genes. {\em BMC Genomics}. \textbf{15}, 1-7 (2014)
\bibitem{gupta2011development}Gupta, S., Kumari, K., Das, J., Lata, C., Puranik, S. \& Prasad, M. Development and utilization of novel intron length polymorphic markers in foxtail millet (Setaria italica (L.) P. Beauv.). {\em Genome}. \textbf{54}, 586-602 (2011)
\bibitem{das2016silico}Das, J. \& Ghosh, T. In-silico studies of micrornas regulation in higher eukaryotes from the perspective of molecular evolution. (Bose Institute,2016)
\bibitem{sen2018exploring}Sen, K., Bhattacharyya, D., Sarkar, A., Das, J., Maji, N., Basu, M., Ghosh, Z. \& Ghosh, T. Exploring the major cross-talking edges of competitive endogenous RNA networks in human Chronic and Acute Myeloid Leukemia. {\em Biochimica Et Biophysica Acta (BBA)-General Subjects}. \textbf{1862}, 1883-1892 (2018)
\bibitem{das2019identification}Das, J., Verma, D., Gustafsson, M. \& Lerm, M. Identification of DNA methylation patterns predisposing for an efficient response to BCG vaccination in healthy BCG-naı̈ve subjects. {\em Epigenetics}. \textbf{14}, 589-601 (2019)
\bibitem{karlsson2021differential}Karlsson, L., Das, J., Nilsson, M., Tyrén, A., Pehrson, I., Idh, N., Sayyab, S., Paues, J., Ugarte-Gil, C., Méndez-Aranda, M. \& Others A differential DNA methylome signature of pulmonary immune cells from individuals converting to latent tuberculosis infection. {\em Scientific Reports}. \textbf{11}, 1-13 (2021)
\bibitem{zhu2021innate}Zhu, G., Azharuddin, M., Islam, R., Rahmoune, H., Deb, S., Kanji, U., Das, J., Osterrieth, J., Aulakh, P., Ibrahim-Hashi, H. \& Others Innate Immune Invisible Ultrasmall Gold Nanoparticles—Framework for Synthesis and Evaluation. {\em ACS Applied Materials & Interfaces}. \textbf{13}, 23410-23422 (2021)
\bibitem{huoman2021mild}Huoman, J., Sayyab, S., Apostolou, E., Karlsson, L., Porcile, L., Rizwan, M., Sharma, S., Das, J., Rosen, A. \& Lerm, M. Mild SARS-CoV-2 infection modifies DNA methylation of peripheral blood mononuclear cells from COVID-19 convalescents. {\em MedRxiv}. (2021)
\bibitem{kalsum2021high}Kalsum, S., Andersson, B., Das, J., Schön, T. \& Lerm, M. A high-throughput screening assay based on automated microscopy for monitoring antibiotic susceptibility of Mycobacterium tuberculosis phenotypes. {\em BMC Microbiology}. \textbf{21}, 1-14 (2021)
\bibitem{singhania2021cd4+}Singhania, A., Dubelko, P., Kuan, R., Chronister, W., Muskat, K., Das, J., Phillips, E., Mallal, S., Seumois, G., Vijayanand, P. \& Others CD4+ CCR6+ T cells dominate the BCG-induced transcriptional signature. {\em EBioMedicine}. \textbf{74} pp. 103746 (2021)
\bibitem{pehrson2021dna}Pehrson, I., Braian, C., Karlsson, L., Idh, N., Danielsson, E., Andersson, B., Paues, J., Das, J. \& Lerm, M. DNA methylation profiling of immune cells from tuberculosis-exposed individuals overlaps with BCG-induced epigenetic changes and correlates with the emergence of anti-mycobacterial'corralling cells'. {\em MedRxiv}. (2021)
\bibitem{das2021dna}Das, J., Idh, N., Sikkeland, L., Paues, J. \& Lerm, M. DNA methylome-based validation of induced sputum as an effective protocol to study lung immunity: construction of a classifier of pulmonary cell types. {\em Epigenetics}. pp. 1-12 (2021)
\bibitem{huoman2021epigenome}Huoman, J., Sayyab, S., Apostolou, E., Karlsson, L., Porcile, L., Rizwan, M., Sharma, S., Das, J., Rosén, A. \& Lerm, M. Epigenome-wide DNA methylation profiling of healthy COVID-19 recoverees reveals a unique signature in circulating immune cells.  (2021)
\bibitem{lundquist2022olfm4}Lundquist, H., Andersson, H., Chew, M., Das, J., Turkina, M. \& Welin, A. The Olfm4-defined human neutrophil subsets differ in proteomic profile in septic shock. {\em BioRxiv}. (2022)
\bibitem{lysiak2022methylome}Lysiak, M., Das, J., Soderkvist, P. \& Malmstrom, A. Methylome analysis of short versus long-term GBM survivors from the Nordic randomised, phase 3 trial. {\em Brain Tumor Research And Treatment}. \textbf{10} (2022)
